---
title: "Unit 1 - 3 Review Starter"
author: "Forest"
date: "Feb 23rd"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand_minerals.csv")
location_descriptions <- read_csv("data/location_descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility_hardness.csv")
```

## Exercises

### Exercise 1


```{r inspect-sand-minerals}
glimpse(sites)

names(sites)
```

There are 23 rows and 2 variables. 

What each row means is the location at which of the 10 locations each mineral is found at.

### Exercise 2

```{r inspect-other-dataframes}
glimpse(density)
glimpse(solubility_hardness)
glimpse(location_descriptions)

```

Density has 3 rows and 2 columns, solubility_hardness has 3 rows and 3 columns, and location_descriptions has 10 rows and 2 columns. 

Each row in this data set are the minerals(Quartz, Feldspar, Biotite), and the locations(1-10
.
```{r variable-names}
names(density)
names(solubility_hardness)
names(location_descriptions)
```

### Exercise 3

```{r join-mineral-properties}
density %>% 
  full_join(sites)

```


### Exercise 4

Remove this text, and add your answer for Exercise 4 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

## Part II - Data Visualization

`starwars` is already loaded within the `dplyr` package (within `tidyverse`)

### Exercise 7

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 8

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk (Find me if you can :)).
Do not use spaces in code chunk labels.

### Exercise 9

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
